### 2017-09-27 1/exams/m1.tex

\censorruleheight=0ex
\StopCensoring

@@

\begin{center}
  {\Large {\bf CMSC 131A, Midterm 1 (Practice)}\\
    \ \\
    Fall 2017}
\end{center}

@@

@@

@@

\noindent
{\bf Problem 2 (10 points).}
%
The graphical text editor you developed in a recent assignment has
garned major attention by Bay-area venture capitalists who want to
base a start-up company around your editor.  They're ready to invest
to help you develop a full-featured prototype.  But before they write
a check, they want to make sure you can handle fancy operations for
expert text editor users.  They ask if you can implement a
\emph{transpose} operation, which will transpose the character to the
left of a cursor with the character to the right of the cursor.  To
satisfy your potential investors, you define the following function
for transposing characters at a given position in a string that has at
least 2 characters in it:
\begin{verbatim}
;; transpose : String Index -> String
;; Transpose characters at index i and i+1.
;; Assumes string has length >= 2 and 0<=i, i+1<=length.
(check-expect (transpose "ab" 0) "ba")
(check-expect (transpose "peice" 1) "piece")
(check-expect (transpose "student's" 7) "students'")
(define (transpose s i) ...)
\end{verbatim}

@@

@@

@@

@@

@@

>>>>

\censorruleheight=0ex
%\StopCensoring

@@

\begin{center}
  {\Large {\bf CMSC 131A, Midterm 1 (Practice)}\\
    \censor{{\bf SOLUTION}} \ \\
    \ \\
    Fall 2017 \ \\
  }
\end{center}

@@

\begin{SaveVerbatim}{VerbEnv}  
SOLUTION:
(add1 (cond [(= (w 2) 12) 4] [else 9]))   -->[plug]
                ^^^^^                                    
(add1 (cond [(= (* R 2) 12) 4] [else 9])) -->[const]
                   ^                          
(add1 (cond [(= (* 9 2) 12) 4] [else 9])) -->[arith]
                ^^^^^^^           
(add1 (cond [(= 18 12) 4] [else 9]))      -->[arith]
             ^^^^^^^^^            
(add1 (cond [#false 4] [else 9]))         -->[cond]
      ^^^^^^^^^^^^^^^^^^^^^^^^^^            
(add1 (cond [else 9]))                    -->[cond]
      ^^^^^^^^^^^^^^^             
(add1 9)                                  -->[arith]
^^^^^^^^                          
10
\end{SaveVerbatim}

\censor{\vspace{-2.5in}}
\censor{%
\noindent\BUseVerbatim{VerbEnv}}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:
(posn-x (cond [(= (string-length "hi") 2) (make-posn 3 4)]
                  ^^^^^^^^^^^^^^^^^^^^                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [(= 2 2) (make-posn 3 4)]
               ^^^^^^^                                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [#true (make-posn 3 4)]
        ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^       
              [else (make-posn 8 0)]))                     -->[arith]
              ^^^^^^^^^^^^^^^^^^^^^^^         
(posn-x (make-posn 3 4))              
^^^^^^^^^^^^^^^^^^^^^^^^                                   -->[arith]
3
\end{SaveVerbatim}

\censor{%
\noindent\BUseVerbatim{VerbEnv}}

@@

\noindent
{\bf Problem 2 (10 points).}
%
The graphical text editor you developed in a recent assignment has
garned major attention by Bay-area venture capitalists who want to
base a start-up company around your editor.  They're ready to invest
to help you develop a full-featured prototype.  But before they write
a check, they want to make sure you can handle fancy operations for
expert text editor users.  They ask if you can implement a
\emph{transpose} operation, which will transpose the character to the
left of a cursor with the character to the right of the cursor.  To
satisfy your potential investors, you define the following function
for transposing characters at a given position in a string that has at
least 2 characters in it:
\begin{verbatim}
;; transpose : String Index -> String
;; Transpose characters at left and right of index i.
;; Assumes string has length >= 2 and 1<=i, i+1<=length.
(check-expect (transpose "ab" 1) "ba")
(check-expect (transpose "peice" 2) "piece")
(check-expect (transpose "student's" 8) "students'")
(define (transpose s i) ...)
\end{verbatim}

@@

(define (transpose s i)
  (string-append (substring s 0 (sub1 i))
                 (substring s i (add1 i))
                 (substring s (sub1 i) i)
                 (substring s (add1 i))))
\end{SaveVerbatim}

@@

;; tock : BB -> BB
;; Move ball one tick based on velocity
(check-expect (tock (make-bb "red" (make-posn 2 5) (make-vel 1 -2)))
              (make-bb "red" (make-posn 3 3) (make-vel 1 -2)))
(define (tock bb)
  (make-bb (bb-color bb)
           (make-posn (+ (posn-x (bb-center bb))
                         (vel-deltax (bb-vel bb)))
                      (+ (posn-y (bb-center bb))
                         (vel-deltay (bb-vel bb))))
           (bb-vel bb)))
\end{SaveVerbatim}

@@

\censor{%
\noindent\BUseVerbatim{VerbEnv}}

@@

SOLUTION (there are many, this is just one):

;; A Route is one of:
;; - '()
;; - (cons Seg Route)
;; Interp: list of segments to follow in a truck route

;; A Seg is a (make-seg Turn Number)
(define-struct seg (turn dur))
;; Interp: turn to make immediately,
;; followed by distance dur going straight

'()
(cons (make-seg "L" 50)
      (cons (make-seg "R" 20)
            '()))
\end{SaveVerbatim}

@@

;; cs : ClassGrades -> Natural
;; Count the number of Cs in the class, i.e. numbers in [70,80).
(check-expect (cs '()) 0)
(check-expect (cs (cons 99 (cons 72 (cons 74 (cons 50 '()))))) 2)
(define (cs gs)
  (cond [(empty? gs) 0]
        [(cons? gs)
         (+ (cond [(c? (first gs)) 1]
                  [else 0])
            (cs (rest gs)))]))

;; c? : Grade -> Boolean
;; is the given grade a C (i.e. in [70,80))?
(check-expect (c? 70) #true)
(check-expect (c? 80) #false)
(define (c? g)
  (and (<= 70 g) (< g 80)))
\end{SaveVerbatim}
